Anxiety, avoidance, and sequential evaluation

### 2019-04-14 manuscripts/manuscript/manuscript.tex
making ready for overleaf import

>>>>

Distributional RL, Plagiarized (Bishop 2018)
"Hence, anxious individuals might have even weaker upper bounds than other individuals for probability estimates of rare, extremely negative events. One strategy for robustly avoiding catastrophic failures is to adopt a worse-case scenario (H 1 control) [9], that is, to rely on the upper bound as opposed to the mean or median of the distribution of outcome probabilities. Consistent with this, clinically anxious individuals are reported to engage in catastrophizing, focusing on worst case outcomes [10]"

There is a third that we did not address here: that of the state itself. Here we assumed that states were fully observable; in other words, there was no uncertainty about the state an agent was currently occupying. In partially-observable Markov decision problems, the state itself must be inferred from external and internal variables. This is yet another means by which bad value can spread if undue likelihood is granted to undesirable or aversive states. This ideas has previously been proposed to explain some symptoms in anxiety \citep{Paulus2012}, and not without good reason. Anxiety disorders involve negatively biased interpretation of ambiguous percepts \citep{Hartley2012}, which may result in aberrant planning and increased avoidance for similar reasons to those described above. This is an area for future research.

Model-based
want to build an account about worry, thinking anxiety is correlated with more worry time, and worry is specifically carrying out these sorts of thought patterns.

Berenbaum (2010):
First, lower levels of self-esteem, which might be expected to be associated with lower levels of perceived competence, have been found to be associated with higher levels of worrying (Meyer, Miller, Metzger, & Borkovec, 1990). Second, examining the content of anxiety diaries, Breitholtz, Johansson and Ost (1999) found that individuals with GAD were much more likely to write about doubts concerning their competence than were individuals with panic disorder. Third, Davey and Levy (1999) found that individuals with higher levels of worrying reported that they were more likely to endorse statements concerning personal inadequacy/incompetence when thinking about “ a stressful, traumatic or diffi cult situation.” Fourth, Davey and Levy (1998) found that the more severe the participants' worrying, the more they couched their worries in terms of personal inadequacies. Finally, in two separate studies, Berenbaum, Thompson, and Bredemeier (2007) found that lower levels of perceived competence were associated with higher levels of worry- ing. Further, the link between perceived competence and worrying was mediated by perceived probabilities of undesirable outcomes.

Replay, Plagiarized (Bishop 2018):
"Off-line replay of prior experiences and simulation of counterfactual actions and associated outcomes provide a means to update action values following the occurrence of an extremely negative event [18]. It has been argued that model-based previous states should be prioritized for replay based on how much that replay would change value estimates [34 ]. One way to accomplish this is by tagging states based on how much their successors value has changed [35]. If change in value estimates determines priority for replay, the astronomically large discrepancy in outcome value occasioned by the occurrence of a rare, extremely negative event would be expected to result in prioritized replay of that events antecedents.""
